Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-04-06 CVPR16/Source/applications.tex
Make our use of camera poses and known number of objects clearer

\vspace{-0.3cm}
\paragraph{Continuous point track energy with occlusion}
%\label{sec:totalContPtTracksEnergy}
Let $\relp{i}{t}$ be the pose of object $O_i$ at time $t$ in world coordinates (computed using the camera pose at time $t$ and the relative pose of object $O_i$ with respect to the camera). We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ as the forward and inverse projection functions that project a 3D point to the 2D image and vice versa. Then, the reprojection error for 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that the inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection relies on the object pose at time $t-1$ while the forward projection relies on the object pose at time $t$, which can be different.

>>>>

\vspace{-0.3cm}
\paragraph{Continuous point track energy with occlusion}
%\label{sec:totalContPtTracksEnergy}
Let $\relp{i}{t}$ be the pose of object $O_i$ at time $t$ in world coordinates, which is computed using the camera pose at time $t$ and the relative pose of object $O_i$ with respect to the camera at time $t$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ as the forward and inverse projection functions that project a 3D point to the 2D image and vice versa. Then, the reprojection error for 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that the inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection relies on the object pose at time $t-1$ while the forward projection relies on the object pose at time $t$, which can be different.

### 2016-04-06 CVPR16/Source/experiments2.tex
Make our use of camera poses and known number of objects clearer

For each sequence, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters (position, orientation, and dimensions) of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

>>>>

For each sequence, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. The parameters (position, orientation, and dimensions) of all objects (cars) estimated by the method of \cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering). The number of objects is known a priori in our model (from object tracking~\cite{Choi_Savarese_2010}) and is also provided to other methods such as BBox and RAS.
